\documentclass[margin]{res}

\usepackage{mathpazo}
\usepackage{array,booktabs}

\hoffset = 0.5in
\voffset = -0.75in
\textheight = 11.5in
\setlength{\textwidth}{6.5in}

\newcommand{\fullbar}{\rule{\textwidth}{0.4pt}}

\begin{document}

{\Huge\textbf{Craig Cabrey}}
\vspace{0.25cm}
\newline
102 Usher Lane $\bullet$
North Wales, PA 19454 $\bullet$
cac2573@rit.edu $\bullet$
(267) 663-8355 $\bullet$
linkedin.com/in/craigcabrey \vspace{-0.5cm}
\newline
\fullbar
\vspace{-0.75cm}

\begin{resume}

\section{Objective}  

Aspiring and driven Software Engineering student with several years of
academic, community, and industry experience seeking a full time position
starting in the Fall of 2016.

\section{Education}

{\sl Bachelor of Science \& Master of Science,} Software Engineering
\hfill Expected Summer 2016 \\
\textbf{Rochester Institute of Technology} \hfill Rochester, NY
 
\section{Skills} 

{
\small
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{
    >{\arraybackslash}p{2cm}
    >{\arraybackslash}p{5cm}
    >{\arraybackslash}p{4cm}
    >{\arraybackslash}p{3.75cm}}
    & \textbf{Proficient} & \textbf{Familiar} & \textbf{Foundational} \\ \hline
  \textbf{Languages} & Python, PHP, C\#, Java, SQL & C, Ruby, HTML5, CSS3,
                       JavaScript, bash & Vala, Assembly, Promela, Rust \\ \hline
  \textbf{Technologies} & AngularJS, nodejs, express, Laravel,
                          ASP.NET MVC, Bootstrap & LoopBack, LXC, Docker,
                          Django, SharePoint & GTK, \LaTeX \\ \hline
  \textbf{Platforms} & RHEL, Ubuntu, OS X, Windows & FreeBSD, Android &
                       OpenBSD, Arduino, iOS \\ \hline
  \textbf{Tools} & git, svn, cvs, vim, tmux, UML & autotools, gdb, valgrind,
                   Jenkins, JetBrains IDEs & Xcode, Alloy, mercurial
\end{tabular}
}

\section{Experience}

{\sl Production Engineer Intern} \hfill June 2015 - August 2015 \\
\textbf{Facebook, Inc.}, Menlo Park, CA
\begin{itemize}
    \item[] Developed a suite of open source utilities for the GlusterFS
          distributed file system. Utilities reimplemented standard core
          utilities specifically for the GlusterFS API. Facilitated the
          inception of the project, the implementation, and subsequent open
          source release. Source of the project can be found at
          github.com/gluster/glusterfs-coreutils.
          (C, autotools, libgfapi)
\end{itemize}

{\sl Software Engineer Intern} \hfill May 2014 - August 2014 \\
\textbf{Datto, Inc.}, Norwalk, CT
\begin{itemize}
    \item[] Built a process known as Hardware Independent Restore (HIR) using
          modern engineering practices such as dependency injection, package
          management, principle of least privilege, and in-depth testing.
          Created an internal repository of libraries used to build HIR for
          maximum code reuse across the entire development team. HIR is
          responsible for converting raw image-based backups into virtual
          machine images prepared for production use.
          (Ubuntu, PHP, PHPUnit, composer, GitHub, Jenkins)
\end{itemize}

{\sl DevOps Engineer Intern} \hfill August 2013 - May 2014 \\
\textbf{Datto, Inc.}, Norwalk, CT
\begin{itemize}
    \item[] Introduced automation at various levels of the development
          processes to improve product quality, development efficiency, and
          monitoring of production systems. Also designed and implemented
          replacements for legacy production systems to increase efficiency,
          security, and reliability of the systems.
          (Ubuntu, PHP, Python, bash, MariaDB, JIRA)
\end{itemize}
 
{\sl Software Engineer Intern} \hfill May 2013 - August 2013 \\
\textbf{Vencore, Inc. (formerly The SI Organization)}, King of Prussia, PA
\begin{itemize} 
    \item[] Automated internal business process that previously required over
          500 man hours a year to complete, saving the company thousands of
          dollars in operating costs.
          (C\#, SharePoint, OpenXML SDK)
    \item[] Designed, implemented, and deployed internal security management
          applications responsible for managing employee foreign contacts as
          required by the Department of Defense for defense contractors.
          (C\#, ASP.NET MVC, MSSQL)
\end{itemize} 

{\sl Software Engineer Intern} \hfill May 2012 - August 2012 \\
\textbf{Siemens Industry, Inc.}, Spring House, PA
\begin{itemize}
    \item[] System, integration, and acceptance test execution and development
          for the Research and Development department.
          (IBM Rational ClearCase, PCS 7 OS, APACS OS)
\end{itemize} 

\section{Projects}

\begin{itemize}
    \item \texttt{reaper}: an open source research tool used to classify and
          score repositories which contain engineered software projects. The
          paper is currently pending review for acceptance at the International
          Conference on Software Engineering (ICSE). Technologies utilized
          include Python, MySQL, and the GitHub API.
    \item Rate My Co-op: an application built for RIT students to rate
          their experiences while on co-op. Technologies utilized include
          Python, Selenium, nodejs, LoopBack, and AngularJS.
    \item Self-hosted dynamic DNS: a combination of systems including a FreeBSD
          router, a BIND9 DNSSEC name server, and glue code that works together
          to ensure up to date DNS records for home VPN access.
\end{itemize}

\end{resume}
\end{document}
